---
title: "Full Pay Predicted Probability Comparison"
date: "Feb 13, 2017"
output: html_document
---

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(dplyr)
library(plyr)
library(ggplot2)
library(knitr)
################# QC Scoring ########################
FULLPAY = read.csv("../Desktop/Probability Comparison_FullPay_0213.csv")

# Beyond 3 digit indicator
FULLPAY$ind = ifelse(FULLPAY$PROB_DIFF_ABS>=0.001,1,0)
```

### Overview of the comparison dataset
###### Note that:
###### 1. **PROB_FULLPAY_SCORED** is the scored probability from Full Pay Random Forest model  
###### 2. **PROB_FULLPAY** is calculated through PROB_FULLPAY = 1 - PROB_NFO - PROB_RBO from the NFO/RBO Random Forest model
###### 3. PROB_DIFF = PROB_FULLPAY_SCORED - PROB_FULLPAY
###### 4. PROB_DIFF_ABS is the absolute value of PROB_DIFF
```{r,echo=FALSE}
kable(head(FULLPAY[,1:ncol(FULLPAY)-1],10),align = "c",format = "markdown")
```

### Summary statistics of probability difference
#### 1. Summary table
```{r,echo=FALSE}
summary(FULLPAY$PROB_DIFF,digits = 3)
```
#### 2. Decile table
```{r,echo=FALSE}
prob_diff_quantile = quantile(FULLPAY$PROB_DIFF,probs=seq(0,1,by = 0.1))
kable(as.data.frame(prob_diff_quantile),align = "c")
```

### Summary statistics of probability difference (absolute difference)
#### 1. Summary table
```{r,echo=FALSE}
summary(FULLPAY$PROB_DIFF_ABS,digits = 3)
```
#### 2. Decile table
```{r,echo=FALSE}
prob_diff_quantile_abs = quantile(FULLPAY$PROB_DIFF_ABS,probs=seq(0,1,by = 0.1))
kable(as.data.frame(prob_diff_quantile_abs),align = "c")
```

```{r,echo=FALSE}
FULLPAY_ind = count(FULLPAY$ind)
FULLPAY_ind$Description = ifelse(FULLPAY_ind$x==0,"|Diff|<0.001","|Diff|>=0.001")
FULLPAY_ind$Percentage = FULLPAY_ind$freq / sum(FULLPAY_ind$freq)
FULLPAY_ind_new = FULLPAY_ind[,c(3,2,4)]

FULLPAY$ind_2 = ifelse(FULLPAY$PROB_DIFF_ABS>=0.01,1,0)
FULLPAY_ind_2 = count(FULLPAY$ind_2)
FULLPAY_ind_2$Description = ifelse(FULLPAY_ind_2$x==0,"|Diff|<0.01","|Diff|>=0.01")
FULLPAY_ind_2$Percentage = FULLPAY_ind_2$freq / sum(FULLPAY_ind_2$freq)
FULLPAY_ind_2_new = FULLPAY_ind_2[,c(3,2,4)]
```

### Difference frequency table - Full Pay Probability
#### 1.indicate whether the absolute difference is beyond **three** decimals
```{r,echo=FALSE}
kable(FULLPAY_ind_new,align="c")
```

#### 2.indicate whether the absolute difference is beyond **two** decimals
```{r,echo=FALSE}
kable(FULLPAY_ind_2_new,align="c")
```

### Histogram plot on Probability Difference
```{r,echo=FALSE}
hist(FULLPAY$PROB_DIFF,col="grey",breaks = 100,main="Full Pay Probability Differennce",
     xlab="Probability Difference")
```

### Boxplot on Probability Difference
```{r,echo=FALSE}
boxplot(FULLPAY$PROB_DIFF,main="Full Pay Probability Difference",horizontal = T)
```









